---
title: ""
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)
library(flexdashboard)
library(plotly)
library(tidyverse)
library(brazilmaps)
library(RColorBrewer)
library(leaflet)
library(readr)
library(gridExtra)
library(kableExtra)
library(GADMTools)
# setwd("~/rrg1@de.ufpe.br/UFSM/Dashboards/Soybean")

soy_data <- read_delim("soy_data2018_comp.csv", ";", escape_double = FALSE, trim_ws = TRUE)

soy_data2017 <- read_csv("soy_data2017.csv")



data2018 <- get_brmap("City") %>% 
  rename(CODIGO= City) %>% 
  filter(State==43) %>% 
  left_join(soy_data, by = "CODIGO")  

data2017 <- get_brmap("City") %>% 
  rename(CODIGO= City) %>% 
  filter(State==43) %>% 
  left_join(soy_data2017, by = "CODIGO")  


```

Soybean culture in the Rio Grande do Sul
===================================== 
Column {.tabset}
-----------------------------------------------------------------------

### Production value in 2017
```{r}
my_orange = brewer.pal(n = 9, "Oranges")[2:8]

mytext1 <- rep(NA,497)

for(i in 1:497){
  if(is.na(data2017$production_value[i])==T){
    mytext1[i] <- paste(
  "City: ", data2017$nome[i],"<br/>", 
  "No production in 2017")
  } else{
    mytext1[i] <- paste(
  "City: ", data2017$nome[i],"<br/>", 
  "Production value: ", data2017$production_value[i], " thousands of R$","<br/>", 
  "Produced quantity: ", data2017$soy_production[i], " tonnes" ,"<br/>", 
  "Number of establishments: ",  data2017$number_of_establishments[i], "<br/>", 
  "Average yield: ", round(data2017$average_yield[i],3), " tonnes/ha" ,
  sep="")
  }
}
  
mytext1 <- mytext1   %>%
  lapply(htmltools::HTML)



pal.state <- colorNumeric(palette = my_orange, domain = data2017$production_value)
pal.rev <- colorNumeric(palette = my_orange, data2017$production_value, reverse = TRUE)
m<-leaflet(data2017) %>% 
  addTiles() %>% 
  setView( lat=-30.5, lng=-53 , zoom=7) %>%
  addPolygons(color = "#444444", weight = .5, smoothFactor = 0.5,
              opacity = 1.0, fillOpacity = 0.5,
              fillColor =  ~pal.state(production_value),
              label = mytext1,
              highlightOptions = highlightOptions(color = "white", weight = 2, bringToFront = TRUE)
  ) %>%
  addLegend("bottomright", 
            pal = pal.rev,
            values = ~production_value,
            title = "Production value",
            labFormat =  labelFormat(
              transform = function(x) sort(x, decreasing = TRUE)
              ),
    opacity = 1
  )
m
```



### Dispersion plots for 2017
```{r}

dp1 <- ggplot(data2017, aes(x=soy_production, y=production_value, label=City)) +
            geom_point(shape=1)     +
  labs(y = "Production value", x = "Produced quantity ") +
  theme_classic()
dp2 <- ggplot(data2017, aes(x=number_of_establishments, y=production_value, label=City)) +
            geom_point(shape=1)     +
  labs(y = "Production value", x = "Number of establishments") +
  theme_classic()
 dp3 <- ggplot(data2017, aes(x=average_yield, y=production_value, label=City)) +
            geom_point(shape=1)     +
  labs(y = "Production value", x = "Average yield") +
  theme_classic()
  
subplot(ggplotly(dp1),
        ggplotly(dp2),
        ggplotly(dp3), nrows = 3,titleX = T,titleY = T)
```

### Top production values in 2017
```{r}
rank<- soy_data2017 %>% 
  arrange(desc(production_value)) %>%
  select(-CODIGO) 

kable(cbind(Ranking = 1:20, rank[1:20,]), caption = "Top 20 cities with higher soybean production values in 2017 and their corresponding covariates.", align = "c",
      col.names = c("Ranking", "City", "Production value¹", "Soy production²", "Average yield³", "Number of establishments")) %>%
  kable_styling(c("striped"), full_width = F, position = "center") %>%
  footnote(general = "",
           number = c("in x1000 R$; ", "in tonnes;", "in tones/ha")
           )
```


Column {.tabset}
-----------------------------------------------------------------------

### Production value in 2018
```{r}
my_purd = brewer.pal(n = 9, "PuRd")[2:7]
mytext2 <- rep(NA,497)

for(i in 1:497){
  if(is.na(data2018$production_value[i])==T){
    mytext2[i] <- paste(
      "City: ", data2018$nome[i],"<br/>", 
      "No production in 2018")
  } else{
    mytext2[i] <- paste(
      "City: ", data2018$nome[i],"<br/>", 
      "Production value: ", data2018$production_value[i], " thousands of R$","<br/>", 
      "Produced quantity: ", data2018$soy_production[i], " tonnes" ,"<br/>", 
      "Number of establishments: ",  data2018$number_of_establishments[i], "<br/>", 
      "Average yield: ", round(data2018$average_yield[i],3), " tonnes/ha" ,
      sep="")
  }
}

mytext2 <- mytext2   %>%
  lapply(htmltools::HTML)

pal.state2 <- colorNumeric(palette = my_purd, domain = data2018$production_value)
pal.rev2 <- colorNumeric(palette = my_purd, data2018$production_value, reverse = TRUE)
m2<-leaflet(data2018) %>%
  addTiles() %>%
  setView( lat=-30.5, lng=-53 , zoom=7) %>%
  addPolygons(color = "#444444", weight = .5, smoothFactor = 0.5,
              opacity = 1.0, fillOpacity = 0.5,
              fillColor =  ~pal.state2(production_value),
              label = mytext2,
              highlightOptions = highlightOptions(color = "white", weight = 2,
                                                  bringToFront = TRUE)
  ) %>%
   addLegend("bottomright", 
            pal = pal.rev2,
            values = ~production_value,
            title = "Production value",
            labFormat =  labelFormat(
              transform = function(x) sort(x, decreasing = TRUE)
              ),
    opacity = 1
  )
m2
```


### Dispersion plots for 2018
```{r}

dp4 <- ggplot(data2018, aes(x=soy_production, y=production_value, label=City)) +
            geom_point(shape=1)     +
  labs(y = "Production value", x = "Produced quantity ") +
  theme_classic()
  
dp5 <- ggplot(data2018, aes(x=number_of_establishments, y=production_value, label=City)) +
            geom_point(shape=1)     +
  labs(y = "Production value", x = "Number of establishments") +
  theme_classic()
  
dp6 <- ggplot(data2018, aes(x=average_yield, y=production_value, label=City)) +
            geom_point(shape=1)     +
  labs(y = "Production value", x = "Average yield") +
  theme_classic()

subplot(ggplotly(dp4),
        ggplotly(dp5),
        ggplotly(dp6), nrows = 3, titleX = T,titleY = T)
```


### Top production values in 2018

```{r}
rank2<- soy_data %>% 
  arrange(desc(production_value)) %>%
  select(-CODIGO)

kable(cbind(Ranking = 1:20, rank2[1:20,]), caption = "Top 20 cities with higher soybean production values in 2018 and their corresponding covariates.", align = "c",
      col.names = c("Ranking", "City", "Production value¹", "Soy production²", "Average yield³", "Number of establishments")) %>%
  kable_styling(c("striped"), full_width = F, position = "center") %>%
  footnote(general = "",
           number = c("in x1000 R$; ", "in tonnes;", "in tones/ha")
           )
```

About
===================================== 

**Goals**

This dashboard allows us to describe the behavior of some variables related to the soybean production in the Rio Grande do Sul for 2017 and 2018. It was developed as a visualization tool for the data used in the paper entitled ``Modeling soybean production value in the Rio Grande do Sul with GAMLSS'', which is accepted to Communications in Statistics: Case Studies, Data Analysis and Applications, ISSN: 2373-7484.

**The data**

The data are obtained from the Department of Economics and Statistics (DEE) of Rio Grande do Sul and is available in the link http://feedados.fee.tche.br/feedados/. The Rio Grande do Sul has 497 cities, of which 405 had soybean production in 2017 and 418 in 2018.

**Source files**

The current application was implemented in the R Project for Statistical Computing, and the codes are available in the link https://renata-rojasg.github.io/soybean/.